Testing Statistical Graphics

### 2022-06-24 index.qmd
Add outline

abstract: |
  We outline our process and common pitfalls for developing and testing human perception of statistical graphics.

@@

Goal: Integrate information from the design of \cite{clusters,sineillusion,emily-diss,power}.

>>>>

abstract: |
  We outline our process and common pitfalls for developing and testing human perception of statistical graphics. 
  Goal: Integrate information from the design of \cite{clusters,sineillusion,emily-diss,power}.

@@

Importance of testing statistical graphics

# Testing Methods and Engagement

Lineups
You Draw It
Direct Assessment

# Developing a Model
This is the single longest part of the entire testing process

## The Role of Simulation

## Selecting Parameters

# Pilot Testing and Quality Assurance

Test early, test often, and make sure you look at all of your plots!!!
If you're generating new data for each participant, be sure to save that data to a database so that you can at least see where/how things went wrong!

# Gathering and Analyzing Additional Information

Calculator observations
Scratchpad
Explanation
Confidence Level
User Interactions
Browser fingerprints

# Building the Application
Shiny is awesome

# Analyzing the Data
Be prepared for surprises
